Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-04 papers/actus2021/article.tex
fix

The Marlowe DSL does not support any notion of records,
the variables can only be of type ``Integer''. In order to
map contract state -- \emph{ContractStatePoly} -- we pack a set of Marlowe
variables of type \texttt{Value} and \texttt{Observation}, representing the previous ($t-1$) state, passing them into
\emph{ContractStatePoly}, to apply the polymorphic state transition, and
finally unpack \emph{ContractStatePoly} into a set of Marlowe variables representing the 
 state at $t+1$:
% SJT again I am confused about t-1 to t+1 transition. Why not just one step?  
% dk14. I'll change that. I imagined t as time of event while t+1 is after event 
\noindent 
\begin{equation*}
st_{t}=unpack(stateTransition(pack(st_{t-1}))),
\end{equation*}
\noindent
where \emph{pack} is a chain of \texttt{UseValue} constructs and \ident{unpack} is a chain of
\texttt{Let}s.

>>>>

The Marlowe DSL does not support any notion of records,
the variables can only be of type ``Integer''. In order to
map contract state -- \emph{ContractStatePoly} -- we pack a set of Marlowe
variables of type \texttt{Value} and \texttt{Observation}, representing the previous ($t-1$) state, passing them into
\emph{ContractStatePoly}, to apply the polymorphic state transition, and
finally unpack \emph{ContractStatePoly} into a set of Marlowe variables representing the 
 state at $t$:
% SJT again I am confused about t-1 to t+1 transition. Why not just one step?  
% dk14. I'll change that. I imagined t as time of event while t+1 is after event 
\noindent 
\begin{equation*}
st_{t}=unpack(stateTransition(pack(st_{t-1}))),
\end{equation*}
\noindent
where \emph{pack} is a chain of \texttt{UseValue} constructs and \ident{unpack} is a chain of
\texttt{Let}s.
